---
title: "Introduction to svGUI: Manage R GUIs in a central place"
author: "Philippe Grosjean"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to svGUI}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

R is designed to be used in different ways. The "Command Line Interface" (CLI) is a first way to interact with R. However, R also supports various "Graphical User Interfaces" (GUI), like **RGui.exe** on Windows, **R.app** on MacOS, RStudio, etc. It also provides bridge to a few graphical toolkits or widgets, namely **Tk** and **Gtk2**. Other GUIs are build using these widgets, like **R Commander**. However, the different GUI items are not always collaborating well with each other, and it is sometimes hard to know which GUI is currently running in the R environment.

Moreover, GUIs are sometimes criticized for leading to not reproducible analyses, because they imply user interaction. It is sometimes useful to be able to tune off GUI actions in a script, in order to make it run non-interactively, and in a reproducible way (providing you give a default value that can be used for the tests).

**svGUI** solves these two problems by exposing information and status about running GUIs in R in a central place, and by allowing to by-pass GUI elements like modal dialog boxes on request, for one or all running GUIs. Here is how.


# Central location for GUI information and status

**svGUI** uses a 'gui' S3 object to store information about a GUI. This object is located on the search path^[All the 'gui' objects are stored in an environment called `SciViews:TempEnv` that is attached to the search path.]. It is basically a sub-classed environment that contains different objects. When loading **svGUI**, one default 'gui' object is created, named `.GUI`:

```{r}
library(svGUI)
.GUI
```

This object contains various information about GUI items it uses (none for the moment):

```{r}
names(.GUI)
```

A frequently-used GUI item is a **modal dialog box**, a dialog box prompting for some data and that blocks the R script until it is dismissed. (see **svDialogs** for such **svGUI**'s compatible dialog boxes). For instance, an input box would prompt for your name. An **svGUI**-compatible dialog box will report its state, message and result in its corresponding 'gui' object at several occasions:

1. When the dialog box is initialized,
2. When the user changes something in the dialog box,
3. When the dialog box is closed (either with the **OK** button, or perhaps, cancelled with a **Cancel** button),
4. If, for some reasons, an error occurred,
5. Finally, if the dialog box is **by-passed**, providing a default value instead.

So, the state of the dialog box is accessible in our 'gui' object.

Case 5 requires a little bit more of explanation, here under.


# Inactivate modal dialog boxes

**svGUI** gives full power to the end-user: he can decide to inactivate (by-pass) modal dialog boxes. So, in our example, the input box would not be displayed. Of course, the code must be designed to give a default value that is suitable for the rest of the process in that case, say, a generic name. It is the responsibility of the dialog box designer to provide a way to gracefully by-pass the dialog box.

In order to tell that you don't want to be interrupted in your GUI, you just change the `gui_ask()` property to `FALSE`:

```{r}
gui_ask(.GUI)
# Turn the ask property off, so that the GUI does not interrupt R any more
gui_ask(.GUI) <- FALSE
gui_ask(.GUI)
```


## GUI management and examples

You  can create as many different 'gui' objects as you want. They can differ by the GUI widgets you use (set by its `widgets` property), or can be prohibited individually to interrupt R, using `gui_ask()`. Use `gui_list()` to get the list of all currently active GUIs.

```{r}
gui_add("tk_gui", widgets = "tcltk", ask = TRUE)
gui_list()
```

Now, the 'gui' object does nothing by itself. It only centralizes key information about your GUI items. You must use (or design) **svGUI** compatible code to make something useful with it. _For a good example of a series of dialog boxes using the 'gui' object, take a look at the **svDialogs** package._
