---
title: "SPARROW"
author: "Richard Alexander and Lillian Gorman-Sanisaca"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is where we will put an introduction to the `RSPARROW` package in general terms.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
[comment]: <> (This is a comment, it will not be included the "#" indicates a section title, different levels of titles can be specified by more "##")
#Loading RSPARROW

Start by loading the package. Since this is not a real package we cannot call library(SPARROW) here.

```{r, eval=FALSE}
  ############################
  ### 1. SET MAIN PATHNAME ###
  ############################

path_main <- "S:/R_SPARROW/R_SPARROW_master"

#results, data, and gis directories should be in the same folder at the same level
results_directoryName<-"results"
data_directoryName<-"mydata"
gis_directoryName<-"gis"

  ###############################
  ### 2. Load the R functions ###
  ###############################
  
  # Install required packages
  #   this is a one time process unless a new version of R is installed
  #   packages previously installed by user will be skipped

  if_install_packages<-"no"
     #run these 3 lines together to install packages
     source(paste(path_main,"/R/installPackages.R",sep=""))
     installPackages(if_install_packages)
  
  # Load RSPARROW functions (These 2 lines should ALWAYS be run together)
     suppressWarnings(remove(list=c("saved","runScript","run2","runRsparrow")))
     devtools::load_all(path_main,recompile = FALSE) 
```

#Setting up control files

Here we can put description of the control files.  If this becomes a real package then we can include data and instruct the user to load it and even use it as default for the primary function.  We can also display data.

##Example parameters file
```{r,echo=FALSE}
structure(list(sparrowNames = c("point", "ndep", "MANC_N", "FARM_N", 
"Fixation", "ldrainden", "PPT30MEAN", "meanTemp", "tiles_perc", 
"soil_CLAYAVE", "rchdecay1", "rchdecay2", "rchdecay3", "iresload"
), description = c("Municipal/industrial point source ", "Atmospheric deposition N (wet only)", 
"Livestock manure N", "Fertilizer N use", "Cropland area (fixation-related)", 
"Drainage density (km/km2)", "Precipitation (annual mean)", "Air temperature (annual mean)", 
"Tile drainage (fraction of area)", "Soil clay content (fraction of area)", 
"Small stream decay (mean Q<1.13 m3/s)", "Medium stream decay (1.13 m3/s < mean Q < 1.93 m3/s)", 
"Large stream decay (mean Q > 1.93 m3/s)", "Reservoir decay (areal hydr. Load)"
), parmUnits = c("fraction, dimensionless", "fraction, dimensionless", 
"fraction, dimensionless", "fraction, dimensionless", "kg/ha/yr", 
"dimensionless", "mm/yr", "degrees C.", "dimensionless", "dimensionless", 
"per day travel time", "per day travel time", "per day travel time", 
"meters/year"), parmInit = c(0.5, 0.1, 0.1, 0.1, 1, 0.1, 0.01, 
0.01, 1, 0.01, 0.1, 0.1, 0.1, 1), parmMin = c(0, 0, 0, 0, 0, 
-10000, -10000, -10000, -10000, -10000, 0, 0, 0, 0), parmMax = c(1000, 
1000, 1000, 1000, 1000, 10000, 10000, 10000, 10000, 10000, 1000, 
1000, 0, 20), parmType = c("SOURCE", "SOURCE", "SOURCE", "SOURCE", 
"SOURCE", "DELIVF", "DELIVF", "DELIVF", "DELIVF", "DELIVF", "STRM", 
"STRM", "STRM", "RESV"), parmScale = c(10, 10, 10, 10, 1, 10, 
100, 100, 1, 100, 1, 1, 1, 1), parmConstant = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), parmCorrGroup = c(0, 1, 1, 0, 0, 
1, 1, 0, 1, 1, 0, 0, 0, 0)), .Names = c("sparrowNames", "description", 
"parmUnits", "parmInit", "parmMin", "parmMax", "parmType", "parmScale", 
"parmConstant", "parmCorrGroup"), class = "data.frame", row.names = c(NA, 
-14L))
```

This is how we include a code chunk. Used documented function as example.

```{r, eval=FALSE}
x<-c(1,2,3)
y<-c(NA,4,5)
replaceNAs(named.list(x,y))
```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
