---
title: "`r params$file.output.list$run_id`"
author: ""
date: "`r paste0('Output on ',format(Sys.time(), '%m-%d-%Y'))`"
output: html_document
params:
  file.output.list: file.output.list
  predictMapType: predictMapType
  GeoLines: GeoLines
  plotShape: plotShape
  k: k
  existGeoLines: existGeoLines
  Rshiny: Rshiny
  input: input
  predictionTitleSize: predictionTitleSize
  scenario_name: scenario_name
  scenario_map_list: scenario_map_list
  master_map_list: master_map_list
  predictionLegendSize: predictionLegendSize
  mapunits.list: mapunits.list
  predictionLegendBackground: predictionLegendBackground
  break1: break1
  Mcolors: Mcolors
  enable_plotlyMaps: enable_plotlyMaps
  output_map_type: output_map_type
  lineWidth: lineWidth
  lon_limit: lon_limit
  lat_limit: lat_limit
  nlty: nlty
  nlwd: nlwd
  mapdataname: mapdataname
  predictionMapColors: predictionMapColors
  add_plotlyVars: add_plotlyVars
  mapScenarios: mapScenarios
  predictionMapBackground: predictionMapBackground
  LineShapeGeo: LineShapeGeo
  mapvarname: mapvarname
  predictionClassRounding: predictionClassRounding
  commonvar: commonvar
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,eval=TRUE, echo=FALSE,warning=FALSE, message = FALSE)
```

```{r, eval=TRUE, echo=FALSE,warning=FALSE, message = FALSE,fig.width=8, fig.height=8}
#unpack params
predictMapType<-params$predictMapType
GeoLines<-params$GeoLines
plotShape<-params$plotShape
k<-params$k
existGeoLines<-params$existGeoLines
Rshiny<-params$Rshiny
input<-params$input
predictionTitleSize<-params$predictionTitleSize
scenario_name<-params$scenario_name
scenario_map_list<-params$scenario_map_list
master_map_list<-params$master_map_list
predictionLegendSize<-params$predictionLegendSize
mapunits.list<-params$mapunits.list
predictionLegendBackground<-params$predictionLegendBackground
break1<-params$break1
Mcolors<-params$Mcolors
enable_plotlyMaps<-params$enable_plotlyMaps
output_map_type<-params$output_map_type
lineWidth<-params$lineWidth
lon_limit<-params$lon_limit
lat_limit<-params$lat_limit
nlty<-params$nlty
nlwd<-params$nlwd
mapdataname<-params$mapdataname
predictionMapColors<-params$predictionMapColors
add_plotlyVars<-params$add_plotlyVars
commonvar<-params$commonvar
mapScenarios<-params$mapScenarios
predictionMapBackground<-params$predictionMapBackground
LineShapeGeo<-params$LineShapeGeo
mapvarname<-params$mapvarname
predictionClassRounding<-params$predictionClassRounding

if (enable_plotlyMaps=="no" | enable_plotlyMaps=="static"){
  
}else{#plotlystuff
  if (!mapScenarios){
    titleStr<-paste0(master_map_list[k],"\n",mapunits.list[k])
  }else{
    if (!Rshiny){
      titleStr<-paste(scenario_name,scenario_map_list[k],"\n",mapunits.list[k],sep=" ")
    }else{
      titleStr<-paste(input$scenarioName,master_map_list[k],"\n",mapunits.list[k],sep=" ")
    }
  }
}
if (enable_plotlyMaps=="yes" | enable_plotlyMaps=="plotly"){
  #start plotly plot
  p<-plot_ly() %>%
    layout(
      showlegend =TRUE,
      xaxis = list(range = lon_limit,
                   showticklabels= TRUE,
                   title = "Longitude"),
      yaxis = list(range = lat_limit,
                   showticklabels = TRUE,
                   title = "Latitude"),
      title = titleStr)
}

if (existGeoLines){
  
  if (enable_plotlyMaps=="no" | enable_plotlyMaps=="static"){
    plot(st_geometry(GeoLines),lwd=0.1,xlim=lon_limit,ylim=lat_limit,col = predictionMapBackground)
  }else if (enable_plotlyMaps=="yes" | enable_plotlyMaps=="plotly"){
    p <- p %>% add_sf(data = GeoLines,  mode = "lines", type = "scatter",
                      stroke = I("black"),color = I(predictionMapBackground),
                      name = LineShapeGeo, hoverinfo = "none")
    
    
    
  }
}




# select the shading colors for a given mapping variable

if (enable_plotlyMaps=="no" | enable_plotlyMaps=="static"){
  mapvarname <- paste0("plotShape$MAPCOLORS",k)
  if (existGeoLines){
    if (predictMapType=="stream"){
      xtext <- paste0("plot(st_geometry(plotShape),col=",mapvarname,",lwd=lineWidth, add=TRUE)")
    }else{#catchment
      xtext <- paste0("plot(st_geometry(plotShape),col=",mapvarname,",lwd=0.01, lty=0, add=TRUE)")
    }
    eval(parse(text=xtext))
  } else {
    if (predictMapType=="stream"){
      xtext <- paste0("plot(st_geometry(plotShape),col=",mapvarname,",lwd=lineWidth,bg = predictionMapBackground)")
    }else{#catchment
      xtext <- paste0("plot(st_geometry(plotShape),col=",mapvarname,",lwd=0.01, lty=0,bg = predictionMapBackground)")
    }
    eval(parse(text=xtext))
  }
}else if (enable_plotlyMaps=="yes" | enable_plotlyMaps=="plotly"){#plotly
  mapvarname <- paste0("MAPCOLORS",k)
  suppressWarnings(remove(list = c(add_plotlyVars)))
  uniqueCols<-eval(parse(text = paste0("as.character(unique(plotShape$",mapvarname,"))")))
  uniqueCols<-Mcolors[Mcolors %in% uniqueCols]
  for (c in uniqueCols){
    plotShape$mapColor<-eval(parse(text = paste0("plotShape$",mapvarname)))
    mapdata<-plotShape[plotShape$mapColor==c,]
    mapdata$mapdataname<-eval(parse(text = paste0("mapdata$",mapdataname)))   
    
    
    lineText<-"~paste('</br> ',master_map_list[k],' :',
                   round(mapdataname,predictionClassRounding)"
    
    lineText<-addMarkerText(lineText,add_plotlyVars,mapdata, mapdata)$markerText
    
    if (predictMapType=="stream"){
      p <- p %>% add_sf(data = mapdata, mode = "lines", type = "scatter",
                        color = I(c),
                        name = break1[k][[1]][uniqueCols==c],
                        line = list(width = lineWidth),
                        hoverinfo = 'text',
                        text = eval(parse(text = lineText)))
    }else{#catchment
      p <- p %>% add_sf(data = mapdata[1,],  
                        type = "scatter", mode = "lines",
                        # color = toRGB(c),
                        opacity = 1,fillcolor = toRGB(c),
                        line = list(color = toRGB(c),width = 0.8, opacity = 1),
                        name = break1[k][[1]][uniqueCols==c],
                        hoverinfo = 'text',
                        split = eval(parse(text = paste0("~",commonvar))),
                        hoveron = "fills",
                        legendgroup = c,
                        text = eval(parse(text = lineText)),
                        showlegend = TRUE)
      p <- p %>% add_sf(data = mapdata[2:nrow(mapdata),],  
                        type = "scatter", mode = "lines",
                        # color = toRGB(c),
                        opacity = 1,fillcolor = toRGB(c),
                        line = list(color = toRGB(c),width = 0.8, opacity = 1),
                        hoverinfo = 'text',
                        split = eval(parse(text = paste0("~",commonvar))),
                        hoveron = "fills",
                        legendgroup = c,
                        text = eval(parse(text = lineText)),
                        showlegend = FALSE)
    }
  }
}else{#leaflet
  mapvarname <- paste0("MAPCOLORS",k)
  suppressWarnings(remove(list = c(add_plotlyVars)))
  uniqueCols<-eval(parse(text = paste0("as.character(unique(plotShape$",mapvarname,"))")))
  uniqueCols<-Mcolors[Mcolors %in% uniqueCols]
  plotShape$mapColor<-eval(parse(text = paste0("plotShape$",mapvarname)))
  mapdata<-plotShape
  mapdata$mapdataname<-eval(parse(text = paste0("mapdata$",mapdataname)))     
  
  lineText<-"~paste('</br> ',master_map_list[k],' :',
                   round(mapdataname,predictionClassRounding)"
  
  lineText<-addMarkerText(lineText,add_plotlyVars,mapdata, mapdata)$markerText
  
  lineText<-gsub("~","",lineText)
  
  
  lineTextHTML<-paste0("~lapply(",lineText,",HTML)")
  mapdata<-st_transform(mapdata, crs = 4326)
  mapdata<-st_zm(mapdata, drop = T, what = "ZM")
  if (predictMapType=="stream"){
    p <- mapview(mapdata, fill = F, homebutton = F, popup = NULL, legend = F, viewer.suppress = F) %>% 
      .@map %>% 
      clearMarkers() %>% 
      clearShapes() %>% 
      addPolylines(
        data = mapdata, 
        opacity = 1,
        weight = lineWidth,
        color = ~col2hex(mapColor),
        label = eval(parse(text = lineTextHTML))
      ) %>% 
      addLegend("bottomleft", labels = break1[k][[1]], colors = col2hex(uniqueCols),
                title = titleStr, opacity = 1)
  }else{#catchment
    p <- mapview(mapdata, fill = F, homebutton = F, popup = NULL, legend = F, viewer.suppress = F) %>% 
      .@map %>% 
      clearMarkers() %>% 
      clearShapes() %>% 
      addPolygons(
        data = mapdata, 
        stroke = T, 
        color = 'grey', 
        weight = 1, 
        layerId = ~waterid, 
        fillColor = ~col2hex(mapColor),
        fillOpacit = 0.9,
        label = eval(parse(text = lineTextHTML))
      ) %>% 
      addLegend("bottomleft", labels = break1[k][[1]], colors = col2hex(uniqueCols),
                title = titleStr, opacity = 1)
    
  }
}#end leaflet


if (enable_plotlyMaps=="no" | enable_plotlyMaps=="static"){
  if (!mapScenarios){
    title(master_map_list[k],cex.main = predictionTitleSize)
  }else{
    if (!Rshiny){
      title(paste(scenario_name,scenario_map_list[k],sep=" "))
    }else{
      title(paste(input$scenarioName,master_map_list[k],sep=" "),cex.main = predictionTitleSize) 
    }
  }
  
  
  
  legend("bottomleft",break1[k][[1]],lty=nlty,cex=predictionLegendSize,title=mapunits.list[k],
         bg=predictionLegendBackground,lwd=nlwd, col=Mcolors[1:length(break1[k][[1]])], bty="o")
  
  
  
}else{
  p
}


